\pagebreak
\section{Project Description}

The goal of this project is to design and implement an online retail database that functions similarly to the online portals of major retailers such as Walmart, The Home Depot, and Amazon.  This database system is to manage all aspects of online retail operations from product acquisition and warehousing, to customer order fulfillment and followup.  By implementing this database, the online retailer will be able to better understand product turnover, supply chain, human resourcing, fulfillment efficiency, and many other key performance indicators.

From the vendor side of the business, the database will manage the supply chain.  This will allow the business to ensure that its resources are applied as efficiently as possible.  The business will be able to understand how long it will take for each incoming order to be fulfilled so they can plan for the correct amount of warehouse space to be allocated for each order.  Additionally, the business will be able to choose multiple different vendors to aggregate supply capacity in the case that there are supply chain breakdowns.  This will minimize the chance for an interruption in the business's ability to fulfill orders to their customers.

Of course, as an online retail business, customers need to be carefully managed.  This database will facilitate the management of customer accounts, transactions, order fulfillment, and purchase habits.  By tracking these items, the business will be better equipped to manage their inventory, vendors, and sales trends.  By managing customer transactions, the business will be able to make informed decisions about how to manage its supply chain; the business will know how much of each product to order from its vendors.  As an added value to customers, the database will also allow customers to comment and review the products they order and their general experience with the business.

Lastly, and possibly most importantly, this project will manage internal operations.  This includes, but is not limited to, inventory management, warehousing and distribution, human resources and capital resources.  With this system, the business will be able to manage its staffing requirements and responsibilities, which warehouses to use when fulfilling customer orders, management and administrative hierarchy, and working capital.  This will allow the business to maintain smooth operations by ensuring proper staffing at all of its locations.  Furthermore, the business will be able to resource its distribution network to ensure timely and efficient fulfillment of orders.  Finally, the database will be able to support multiple roles for employees to ensure a separation of duties.