\documentclass{article}
\usepackage{titlesec}

\renewcommand{\thesection}{\Roman{section}}
\titleformat
{\section}
[hang]
{\bfseries\Large}
{Section \thesection:} % label
{0.5em}{}

\begin{document}

\begin{titlepage}
\begin{center}
	\vspace*{1cm}
	\Huge
	\textbf{Online Retail Database}
	
	\vspace{1.5cm}
	\LARGE
	\textbf{Mark Kim}
	
	\Large
	Student ID: 918204214
	
	GitHub Username: mkim797
	
	\large
	\vspace{1cm}
	\begin{tabular}{ | l | c | }
		\hline
		\textbf{Milestone/Version} & \textbf{Date}\\
		\hline
		M1V1 & 09/11/2020\\
		\hline
	\end{tabular}

\end{center}
\end{titlepage}

\tableofcontents
\pagebreak

\section{Project Description}
This database system manages all aspects of online retail operations from product acquisition and warehousing, to customer order fulfillment and followup.  Vendors or manufacturers from which the online retailer will purchase product for resale will be managed.  This includes all relevant data that involves order details such as order quantities, cost, fulfillment status, invoicing, purchase history etc.  Similarly, vendor data such as location, contact information, supply capacity, etc.  Internal operations shall be managed as well.  These operations include, but is not limited to, inventory management, customer order fulfillment, human resources, and capital resources.  To complete the product lifecycle, customer relationship management will be an integral part of the database.  Each customer will be tracked, with contact information, purchase history, communication history, product reviews, browsing history, etc.

\section{Use Cases}

\section{Database Requirements}

\section{Detailed List of Main Entities, Attributes and Keys}

\section{Entity Relationship Diagram (ERD)}

\section{Testing Table}

\end{document}